\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage[latin1] {inputenc}
% \usepackage[scale=0.75,top=1cm]{geometry}
\usepackage[scale=0.75, top=1cm, bottom=2cm, footskip=1cm]{geometry}
\linespread{0.9}
%\topmargin .5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 % \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
%\rfoot{{\footnotesize Curriculum Vitae, Camden Bock, \thepage}}
\rfoot{{\thepage}}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\name{{\huge Emilian Joseph Bowry} 
{\newline \footnotesize  07831799619 \quad emil.bowry@icloud.com \quad https://github.com/emilbowry/}
\vspace*{.1in}}

%\title{firstlast_cv2}
\begin{resume}

  % \input{education.tex}


  \section{\sc Experience}
  {\bf AI Compatible} August 2025 - Current\\
  \vspace*{-.1in}
  \begin{itemize}

  \item Developing an automated privacy policy analysis model, this included:
  \begin{itemize} 
  \item  Creating a Suprathreshold Stochastic Resonance (SSR) pipeline to\\ mitigate high-dimensional hubness, effectively amplifying the\\ signal-to-noise ratio of semantically related clusters.
  \item Developing an unsupervised probabilistic consensus engine, integrating \\Expectation-Maximization (EM) and Monte Carlo simulations \\and perturbation analysis to model the topological properties\\of the embedding space.
  \end{itemize}


  \item Redeveloping website, full-stack web development using: Typescript, React,\\ Python, express.js, Prisma, PostgreSQL, mongoDB.
  \item Managing cloud infrastructure, including virtual machines and networking.

  \end{itemize}
  {\bf Luucid.tech} August 2022 - October 2023\\
  Co-founder \\
  \vspace*{-.1in}
  \begin{itemize}
  \item Created novel electrochemical and material mechanisms for detecting\\ spiking-agents in beverages.
  \item  Grant writing to organising a UK wide drug spiking prevalence assessment.
  \end{itemize}

  {\bf Atomic Media} April 2022 - August 2022
  \\Software Development and Business Analyst Intern\\
  \vspace*{-.1in}
  \begin{itemize}
  \item Full stack web development using a variety of languages and technologies.
  \item Analysed new business opportunities and ventures, writing insight articles.
  \item Led skill days, teaching other developers the low-end networking\\ implementations of the technologies they implement:

  \quad https://github.com/emilbowry/NetworkProgrammingLesson/

  \item Organised the weekly cyber-security brief about emerging threats\\ and vulnerabilities.
  \end{itemize}

  \section{\sc Additional Experience}

  {\bf Phasor Average Estimator} 
  \\
  Developed a scale-invariant, Phasor-based Statistical Model to solve hardware jitter and \\Inter-Symbol Interference (ISI), in a Molecular Communication system.
  \vspace*{-.1in}


  {\bf Neural Data Analysis} 
  \\
  Built a simulation system for Lateral Intraparietal Cortex (LIP)\\ neurons to evaluate and test different statistical models for neuron impulses. 

  Used tools, Hidden Markov Models (HMMs), Peri-Stimulus Time Histogram (PSTH),\\ Fano-Factor. Used Bayesian Inference to evaluate model brittleness and mismatch.


  {\bf Integrated Design Project} 
  \\  Group Project building a self-navigating robot - my contributions to the software \\lead us to coming 2nd place in a
  University wide robotics competition.
  \vspace*{-.1in}


  \section{\sc Published and Open Source Software \\  \small{(See github)}}

  {\bf Plotting Tools} 
  \\Extension of the python Plotly library to conveniently visualise 4-dimensional\\ datasets. Using metaprogramming techniques to create a robust and adaptable \\framework.
  \vspace*{-.1in}

  {\bf Code Editor} 
  \\
  A fork of Microsoft VSCode, code editor with telemetery and LLM integrations \\removed, along with some additional features.

  {\bf Monochrome} 
  \\
  Fork of the Black code-formatter. 
  \section{\sc Awards and Achievements}
  {\bf Goldman Sachs} \\ 
  Awarded a scholarship and Engineering Spring week.
  \vspace*{-.1in}

  {\bf Imperial College London} \\
  Awarded the President's Scholarship to Imperial College London,\\ given to the top 112 candidates that demonstrated the highest\\
  academic excellence at interview.
  \\ \\

  Referees available upon request

\end{resume}
\end{document}
