% chktex-file 8
\section{Experience}
\employer{AI Compatible}
\location{Remote}
\dates{August 2025 - Current}
\title{\textbf{Software Developer}}
\begin{position}
    \vspace*{-.1in}
    \begin{itemize}
        \item Developing an automated privacy policy analysis model, this included:
        \begin{itemize} 
            \item  Creating a Suprathreshold Stochastic Resonance (SSR) pipeline to mitigate high-dimensional hubness, effectively amplifying the signal-to-noise ratio of semantically related clusters.
            \item Developing an unsupervised probabilistic consensus engine, integrating\\ Expectation-Maximization (EM) and Monte Carlo simulations and perturbation analysis to model the topological properties of the embedding space.
        \end{itemize}
        \item Redeveloping website, full-stack web development using:\\ Typescript, React Python, express.js, Prisma, PostgreSQL, mongoDB.
        \item Managing cloud infrastructure, including virtual machines and networking.
    \end{itemize}
\end{position}


\employer{Luucid.tech}
\location{Cambridge}
\dates{August 2022 - October 2023}
\title{\textbf{Co-founder}}
\begin{position}
    \vspace*{-.1in}
    \begin{itemize}
        \item Created novel electrochemical and material mechanisms for detecting spiking agents in beverages.
        \item  Grant writing to organising a UK wide drink spiking prevalence assessment.
    \end{itemize}
\end{position}

\employer{Atomic Media}
\location{Nottingham}
\dates{April 2022 - August 2022}

\title{\textbf{Software Development and Business Analysis Intern}}
\begin{position}
    \vspace*{-.1in}
    \begin{itemize}
        \item Full stack web development using a variety of languages and technologies.
        \item Analysed new business opportunities and ventures, writing insight articles.
        \item  Led skill days, teaching other developers the low-end networking implementations of the technologies they implement:  %{\newline \indent https://github.com/emilbowry/NetworkProgrammingLesson/}
            {\begin{itemize} \vspace*{-.05in} \item[] \url{https://github.com/emilbowry/NetworkProgrammingLesson}\end{itemize}}
        \item Organised the weekly cyber-security brief about emerging threats and vulnerabilities. 
    \end{itemize}
\end{position}