% chktex-file 8
\employer{AI Compatible}
\location{Remote}
\dates{August 2025 - Current}
\title{\textbf{Software Developer}}
\begin{position}
    \vspace*{-.1in}
    \begin{itemize}
        \item \textbf{Regulatory Analysis Engine:}
        \begin{itemize} 
        \item Utilises Large Language Models for initial data extraction:  Defining the output form using an OpenAPI schema object for consistently returned format for processing.
        \item Improving and refining the Hader et al's methodology [DOI: 10.1007/s00607-024-01331-9] for a generative, and automatable process to gain more nuanced insight into privacy policy and reduce the amount of API calls.
        \item Unsupervised semantic equivalence detection model utilises Baysian Inference, Topology, Linear Algebra, NLP techniques and Non-linear Systems analysis. Part of my system derived an analog for Random k Conditional Nearest Neighbours, a recently published technique for the classification of high-dimensional data.

        \end{itemize}
        \item \textbf{Redeveloping full-stack website:}
            \begin{itemize} 
                \item Implemented a custom SVG-to-Bitmap rasterizer with memoization to render complex tessellations efficiently.
                \item Created a Perturbation-Based Convergence Algorithm to detect and resolve oscillations caused by circular dependencies between content size and container constraints.
                \item Derived a coordinate transformation system to map Non-Orthogonal Lattices onto Cartesian grids using affine transformations.
                \item Utilised Dimensional Analysis to achieve area-invariant scaling across non-standard aspect ratios.
                \item Modeled layout states as elements of the p2mg Wallpaper Group, proving isomorphisms between distinct stacking configurations to derive a unified  $O(1)$ generation algorithm without iterative solvers.
            \end{itemize}
    \begin{itemize}
    \item Engineered a raw ISO 32000 Serialization Engine: that recursively maps JSON data structures into the PDF coordinate system.

    \end{itemize}

    \end{itemize}
\end{position}

