% chktex-file 8
\employer{AI Compatible}
\location{Remote}
\dates{August 2025 - Current}
\title{\textbf{Software Developer}}
\begin{position}
    \vspace*{-.1in}
    \begin{itemize}
        \item \textbf{Regulatory Analysis Engine:}
        \begin{itemize} 
        \ifattr{math_based}{
            \item Improving and refining the Hader et al's methodology [DOI: 10.1007/s00607-024-01331-9] for a generative, and automatable process to gain more nuanced insight into privacy policy and reduce the amount of API calls.
            \item Unsupervised semantic equivalence detection model utilises Baysian Inference, Topology, Linear Algebra, NLP techniques and Non-linear Systems analysis. Part of my system derived an analog for Random k Conditional Nearest Neighbours, a recently published technique for the classification of high-dimensional data.
        }{
            \item Adapted and improved state-of-the-art research on data extraction from privacy policies.
            \item Devised an unsupervised semantic equivalence detection model of legal statements.
        }
       \end{itemize}
        \item \textbf{Redeveloping full-stack website:}
            \begin{itemize} 
                \ifattr{math_based}{%
                    \item Derived a coordinate transformation system to map Non-Orthogonal Lattices onto Cartesian grids.
                    \item Utilised Dimensional Analysis to achieve area-invariant scaling across all aspect ratios.
                    \item Modeled layout states as elements of the p2mg Wallpaper Group, proving isomorphisms between distinct stacking configurations to derive an $O(1)$ generation algorithm without iterative solvers.
                    \item Implemented an SVG-to-Bitmap rasterizer to render complex tessellations efficiently.
                    \item Created a perturbation-based convergence algorithm to resolve oscillations caused by circular dependencies between content and container size.
                }
                {%
                    \item Style generation: client-side background image generator, CSS geometry engine, generalisation of CSSTypes library
                    \item Direct style-sheet injection to handle high-performance style changes, by prevent re-rendering by modifying css rules and not the elements.
                    \item Contextual telemetry analysis, creates interaction based profiles utilising site-entry points, device and location data to profile user events.
                    \item Managing cloud infrastructure, including virtual machines and networking.% Whats the point
                    \item Devising and prototyping HTTP and API servers from scratch using Rust.%, to learn the fundamentals
                    \item Managing backend API with express.js, Prisma, PostgreSQL, mongoDB.
                }
             
            \end{itemize}
    \begin{itemize}
    \item Engineered an ISO 32000 PDF generator: that maps JSON data structures into a PDF.

    \end{itemize}

    \end{itemize}
\end{position}

